Working with the Poisson distribution

### 2021-09-06 text/21/poisson-inferences.Rmd
More examples of IRR CIs in poisson-inference.Rmd

```{r}
x1 <- 33
T1 <- 290508.9
x2 <- 52
T2 <- 141112
x2 <- 60
T2 <- 100212.3

x1 <- 2
T1 <- 0.6*2*10000

x2 <- 8
T2 <- 5.47*8*10000

r1 <- x1/T1*10000
r2 <- x2/T2*10000
r1
r2
r2/r1
```

@@

```{r}
ln_ratio <- log(x2/x1)
se_ratio <- sqrt(1/x1+1/x2)
se_ratio
ci1 <- c(ln_ratio-1.96*se_ratio, ln_ratio+1.96*se_ratio)
ci1
```

@@

```{r}
ci3 <- ci2/(T2/T1)
round(ci3, 2)
```

@@

>>>>

```{r}
x1 <- 33
T1 <- 290508.9
x2 <- 52
T2 <- 141112
d<- 10000
x2 <- 60
T2 <- 100212.3

x1 <- 2
T1 <- 0.6*2
x2 <- 8
T2 <- 5.47*8
d <- 1

x1 <- 30
T1 <- 54308.7
x2 <- 60
T2 <- 51477.5
d <- 100000

x1 <- 215
T1 <- 4770
x2 <- 84
T2 <- 4193
d <- 1000

r1 <- x1/T1*d
r2 <- x2/T2*d
r1
r2
r1/r2
```

@@

```{r}
ln_ratio <- log(r1/r2)
se_ratio <- sqrt(1/x1+1/x2)
se_ratio
ci1 <- c(ln_ratio-1.96*se_ratio, ln_ratio+1.96*se_ratio)
ci1
```

@@

```{r}
ci3 <- ci2/(T1/T2)
round(ci3, 2)
```

@@

Good example of rate ratio confidence interval calculations

https://pubmed.ncbi.nlm.nih.gov/31895593/

https://pubmed.ncbi.nlm.nih.gov/29637909/

https://storage.googleapis.com/plos-corpus-prod/10.1371/journal.pmed.1001270/1/pmed.1001270.s005.pdf?X-Goog-Algorithm=GOOG4-RSA-SHA256&X-Goog-Credential=wombat-sa%40plos-prod.iam.gserviceaccount.com%2F20210906%2Fauto%2Fstorage%2Fgoog4_request&X-Goog-Date=20210906T225128Z&X-Goog-Expires=86400&X-Goog-SignedHeaders=host&X-Goog-Signature=ae5dde1295ee4d956450c3632eef6f9232594b386e2c4cb01f68bd8e516b25bb05beff6dd146fb84098b1186f3f19cb25b3c8e4c622a11cebfa75bf4a78150761b30984b7f816e1cf9566f7410eac7b9ee45b7a6d77e7b01517eeb36add101d012ba04a50d05d0f50d68097fa8a6b9882b43ab6a93013c066632be8b03b4efc5af597f7fd0ba423c6bd3ceb223847bdcc9f75f8b46cf67ba5ee27ea050855029f5e2c2339e867142d2d82871d9b80c1eb2e91bf06aacfb75ad6fa4f5726ab0ea53ca65e25074a33329eb45146eec575d22f4e324a90e126e1df7b45fc7b58f9246ae863f7f946be73fef76e869d9996ac3ac904d15a4c7bd34eb3777cc1f202a

https://sphweb.bumc.bu.edu/otlt/MPH-Modules/PH717-QuantCore/PH717_ComparingFrequencies/PH717_ComparingFrequencies9.html

https://www.jabfm.org/content/33/4/549.long
